---
output: github_document
bibliography: [packages.bib, literature.bib]
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# croons

<!-- badges: start -->
<!-- badges: end -->

This package implements Croon's correction for multilevel data as outlined by @devlieger2019 using lavaan [@lavaan2012].
This package will not be maintained, because I expect that Yves Rosseel and colleagues will soon make their code publicly available.

## Installation

```{r, eval=FALSE}
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/croons")
```

## Code of Conduct

Please note that the croons project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## References

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c('lavaan'), 'packages.bib')
```
